Secure Composition of Robust and Optimising Compilers

### 2023-07-05 popl/main.tex
Start pass of Sec. 3

\section{Example Properties and their Monitors\pages{3}}\label{sec:compprop}
\Cref{subsec:propdefs} introduces a ,,most general'' trace model and defines properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{cct}) that the case study (\Cref{sec:casestud}) uses.
By means of taking these properties as an example, \Cref{subsec:monitors} defines monitors for them and an agreement relation between a monitor's trace model with the most general trace model.
Then, monitor-based satisfaction is introduced and it is proven that trace-property satisfaction is implied by it.
Since monitor-based satisfaction is easier to reason about, this simplifies later proofs considerably.

\subsection{Most General Trace-Model and Some Property Definitions}\label{subsec:propdefs}

>>>>

\section{Example Properties and their Monitors\pages{3}}\label{sec:compprop}

This section introduces a trace model (\Cref{subsec:propdefs}) that is used to define properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{scct}).
The properties are of practical importance and also of interest in the case study (\Cref{sec:casestud}) this paper presents.
The study uses monitors, which are able to check wether a trace admits a property or not.
The use of monitors is because they have some structure useful for inductive proofs, whereas traces lack this structure, thus making proofs difficult.
So, this section also presents monitors for each of the defined properties (\Cref{subsec:monitors}) and introduces monitor-based satisfaction.
Finally, for each property, it is shown that monitor-based satisfaction implies property satisfaction.

\subsection{Specification Trace Model}\label{subsec:propdefs}
